Simulating Financial Markets using MASON Framework\thanks{Prepared for the 2nd World Congress on Social Simulation, GMU, Fairfax, 14--17 July, 2008.}

### 2008-05-01 documents/WCSS2008Paper/paper.tex
1) Included a mash-up of graphic outputs for article. 2) We have broken the acf functions somewhere, a bug to be corrected

>>>>

\begin{figure}[htbp]
  \begin{center}
   \mbox{
      \subfigure[Ask and bid prices.]{\scalebox{0.5}{\quad \quad \includegraphics[width=0.9\textwidth,height=0.8\textwidth]{../graphics/pricesPlot.pdf}}} \quad
      \subfigure[Raw and absolute returns.]{\scalebox{0.5}{\includegraphics[width=1.00\textwidth]{../graphics/returnPlot.pdf}}}
      }
    \mbox{
      \subfigure[Orderbook shape.]{\scalebox{0.5}{\includegraphics[width=1.00\textwidth]{../graphics/orderbooks.pdf}}} \quad
      \subfigure[Trade volumes.]{\scalebox{0.5}{\includegraphics[width=1.00\textwidth]{../graphics/volumesPlot.pdf}}}
      }
    \mbox{
      \subfigure[Returns histogram.]{\scalebox{0.5}{\includegraphics[width=1.00\textwidth]{../graphics/returnsHistogram.pdf}}} \quad
      \subfigure[Autocorrelation of returns.]{\scalebox{0.5}{\includegraphics[width=1.00\textwidth]{../graphics/acfReturns.pdf}}}
      }
    \caption{Examples of outputs and statistics from a single run of the FinancialModel simulation for default Farmer's parametrization.}
    \label{fig:sampleDynamics}
  \end{center}
\end{figure}
